---
title: "Resume"
author: "Mariana Ozaeta"
output:
  html_document:
    theme: readable
    self_contained: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(results = 'asis', echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(glue)

PDF_EXPORT <- FALSE
links <- c()

source('parsing_functions.R')

position_data <- read_csv('positions.csv', show_col_types = FALSE) %>%
  filter(in_resume) %>%
  mutate(
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions',
      TRUE ~ section
    )
  )
```

<div class="name-block">
# Mariana Ozaeta {.title-name}
Graduate student in Program Evaluation & Data Analytics at Arizona State
University, currently working in nonprofit administration and development
research. I keep donor and program records accurate in Salesforce, research
giving prospects for a development team, and analyze program data in R.

Looking for a program evaluation or data analyst role in the nonprofit or
public sector.
</div>

<div class="resume-grid">

<div class="sidebar">

## Contact

- <i class="fa fa-envelope"></i> mozaeta@asu.edu
- <i class="fa fa-phone"></i> (602) 663-5048
- <i class="fa fa-github"></i> github.com/t00th-blip
- <i class="fa fa-map-marker"></i> Phoenix, AZ

## Skills

```{r}
skills <- tribble(
  ~skill,                  ~level,
  "R / R Markdown",        4,
  "Salesforce",            4,
  "Excel & Google Sheets", 4,
  "Survey & Program Data", 3,
  "SQL",                   2
)
build_skill_bars(skills)
```

## Certifications

- IRB / Human Subjects Research certification
- Salesforce donor records and reporting

## Note

This resume was built for a course assignment (PAF 514). Entries marked
*ASPIRATIONAL ENTRY* are fictional examples, not actual work history.

</div>

<div class="main-col">

## Education

```{r}
position_data %>% print_section('education')
```

## Experience

```{r}
position_data %>% print_section('positions')
```

## Projects

```{r}
position_data %>% print_section('projects')
```

</div>
</div>

```{css, echo=FALSE}
body { max-width: 1000px; }

.name-block { border-bottom: 2px solid #314f96; margin-bottom: 24px; }

h1.title, .name-block h1 {
  color: #314f96;
  font-size: 40px;
  margin-bottom: 8px;
}

.resume-grid {
  display: grid;
  grid-template-columns: 230px 1fr;
  gap: 40px;
}

.sidebar h2, .main-col h2 {
  color: #314f96;
  font-size: 20px;
  border-bottom: 1px solid #ccc;
  padding-bottom: 4px;
  margin-top: 26px;
}

.sidebar ul { list-style: none; padding-left: 0; font-size: 14px; }

.main-col h3 {
  font-size: 17px;
  margin-bottom: 2px;
  color: #222;
}

.main-col p { margin: 2px 0; font-size: 14px; color: #555; }
.main-col ul { margin-top: 6px; font-size: 14px; color: #333; }

.skill-bar {
  color: white;
  padding: 3px 6px;
  margin-bottom: 4px;
  font-size: 13px;
  border-radius: 2px;
  text-shadow: 0 0 2px #333;
}

@media only screen and (max-width: 700px) {
  .resume-grid { grid-template-columns: 1fr; }
}
```
